### 2020-09-18 manuscript/ERL_global_C_review.Rmd
update, we actually did not have enough data for some variables
Update ERL_global_C_review.Rmd

Here, we synthesize ForC data to provide a macroscopic overview of stand-level carbon cycling of the world’s major forest biomes and how it varies with stand age. We address three broad questions:

@@

@@

This review synthesizes data from the ForC database [https://github.com/forc-db/ForC; @anderson-teixeira_carbon_2016, @anderson-teixeira_forc_2018]. ForC amalgamates numerous intermediary data sets (*e.g.*, REFS) and original studies. 
Original publications were referenced to check values and obtain information not contained in intermediary data sets, although this process has not been completed for all records. 
The database was developed with goals of understanding how C cycling in forests varies across broad geographic scales and as a function of stand age. 
As such, there has been a focus on incorporating data from regrowth forests (*e.g.*, Anderson et al 2006, Martin et al 2013, Bonner et al 2013) and obtaining stand age data when possible (83% of records in v.2.0; Anderson-Teixeira et al 2018). 
Particular attention was given to developing the database for tropical forests [@anderson-teixeira_carbon_2016], yet these represented only approximately one-third of records in ForC v.2.0 [@anderson-teixeira_forc_2018]. 
Since publication of ForC v.2.0, we added the following data to ForC: the Global Database of Soil Respiration Database [SRDB v.##; @bond-lamberty_global_2010], the Global Reforestation Opportunity Assessment database (GROA v1.0; Cook-Patton et al. in press; ZenodoDOI), and data from several publications (Taylor et al. 2017, Lutz et al. 2018, Johnson_2018_csss; see GitHub repo for complete list) ([GitHub list](https://github.com/forc-db/ForC/blob/master/database_management_records/ForC_data_additions_log.csv)). 
We note that there remains a significant amount of relevant data that is not yet included in ForC, particularly biomass data from national forest inventories (*e.g.*,: REFS). 
The database version used for this analysis has been tagged as a new release on Github (XX) and assigned a DOI through Zenodo (DOI: TBD).

@@

We drew upon records for *#* annual flux and *#* C stock variables (Table 1). For this analysis, we combined some of ForC’s specific variables (*e.g.*, multiple variables for net primary productivity including various components) into more broadly defined variables (Table 1, [this table](https://github.com/forc-db/ForC/blob/master/figures/C_cycle_diagrams/ForC_variables_mapping_for_C_cycle_diagrams.csv))). 
Although ForC contains information that may be used to standardize or control for methodological differences (*e.g.*, area sampled, min stem diameter sampled, allometric equations applied; Anderson-Teixeira et al 2018), for this analysis we included all relevant data in ForC. 
Throughout ForC, for all measurements drawing from tree census data (*e.g.*, biomass, productivity), the minimum stem diameter sampled was $\le$ 10cm. All records were measured directly or derived from field measurements (as opposed to modeled).

@@

Data were analyzed to produce basic summaries of C cycle patterns across biomes and stand ages following an approach similar to that of Anderson-Teixeira et al (2016). 
For mature forests, to obtain the values reported in the C cycle schematics, we first averaged any repeated measurements within a plot, weighting flux measurements according to the length of measurement periods (*i.e.*, end.date - start.date). 
Values were then averaged across plots clustered within 25 km of one another (geographic.area field of SITES table, sensu Anderson-Teixeira et al 2018), weighting by area.sampled (MEASUREMENTS table) or plot.area (PLOTS table) if available for all records. 
This step was taken to avoid pseudo-replication and to combine any records from sites with more than one name in ForC. 
Finally, for figures 6 and 7, the original values were analyzed via a linear mixed effects model ('lmer' function in 'lme4' R package) with biome as fixed effect and plot nested within geographic.area as random effects on the intercept. 
When Biome had a significant effect, we looked at a Tukey's pairwise comparison to see which biomes were significantly different from one another.

@@

Average C cycles for tropical broadleaf, temperate broadleaf, temperate conifer, and boreal forests $\ge$ 100 years old and with no known major disturbance or significant anthropogenic management are presented in Figures 1-4, and statistics for each biome type are also summarized at: [GitHub URL]. 
Of the 23 flux and 11 stock variables mapped in these diagrams, ForC contained estimates from $\ge$ 7 distinct geographic areas for *#* fluxes and *#* stocks in tropical broadleaf forests, # fluxes and # stocks in temperate broadleaf forests, #fluxes and # stocks in temperate conifer forests, and fluxes and # stocks in boreal forests. 
For variables with records from $\ge$ 7 distinct geographic areas, these ensemble C budgets were generally consistent. 
That is, component fluxes and stocks summed to within 1 std of more inclusive fluxes in all but one instance (in temperate conifer forests, $aboveground woody biomass + foliage biomass > aboveground biomass + 1std$; Fig. 4). **update this: https://github.com/forc-db/ERL-review/issues/16 **

\newpage
\blandscape
```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 2 | C cycle diagram for mature tropical broadleaf forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data. Arrows are scaled as the **square root of flux divided by 5**.", out.width='100%', fig.pos='H'}

@@

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 3 | C cycle diagram for mature temperate conifer forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}

@@

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 4 | C cycle diagram for mature boreal conifer forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}

@@

(**check paragraph with latest data**) The largest C fluxes—including $GPP$, $NPP$, $ANPP$, $BNPP$, $R_{soil_het}$, $R_{soil}$, $R_{eco}$, — were highest in tropical forests, intermediate in temperate (broadleaf or conifer) forests, and lowest in boreal forests  ([ForC_variable_averages_per_Biome](https://github.com/forc-db/ForC/blob/master/numbers_and_facts/ForC_variable_averages_per_Biome.csv)) (Fig. 5). The same held true for some of the subsidiary fluxes: ANPP_foliage, ANPP_woody, [**OTHERS?**]. Other subsidiary fluxes—including NPP_woody, ANPP_repro, ANPP_stem, ANPP_branch, woody.mortality, BNPP_coarse, BNPP_fine,  [**OTHERS?**]—deviated from this pattern and/or lacked data for some biomes. Net ecosystem production ($NEP$) did not follow this pattern, with no significant differences across biomes but the largest (negative) average in temperate broadleaf forests, followed by temperate conifer, boreal, and tropical forests. Thus, C cycling rates generally decreased from tropical to temperate to boreal forests, but with less apparent trends for some of the subsidiary fluxes and an important exception in the overall C balance ($NEP$).

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 5 | Age trends and biome differences in some of the major C fluxes: (a) $GPP$, (b) $NPP$, (c) $ANPP$, (d) $R_{soil}$, (e) $R_{eco}$, and (f) $NEP$. Map shows data sources ($x$ and $o$ indicate young and mature stands, respectively). Lines...  .", out.width='100%', fig.pos='H'}

  knitr::include_graphics("tables_figures/Figure6.png")
```

There were less distinct trends in C stocks across biomes (Fig. 6). Biome means for live aboveground and total biomass followed the same general trend as the major fluxes, with biomass of tropical= temperate broadleaf $\ge$ temperate conifer> boreal forests (Fig. 6a). However, the relative differences in these means were much smaller than for the major C fluxes, and there was significant variation within biomes. Maximum aboveground biomass values followed a very different trend than the means: temperate broadleaf> temperate conifer>boreal>tropical. There were some statistically significant biome differences in less frequently sampled C stocks (*e.g.*, woody biomass, foliage biomass, deadwood), but given high within-biome variability in C stocks and relatively low sample sizes, these were likely attributable to sampling biases and methodological differences than to true differences across biomes.

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 6 | Age trends and biome differences in some of the major forest C stocks: (a) aboveground biomass, (b) foliage, (c) fine roots, (d) dead wood.", out.width='100%', fig.pos='H'}

  knitr::include_graphics("tables_figures/Figure7.png")
```

@@

(**check paragraph with latest data**) Average C cycles for forests <100 years old are presented in Figures 7-10. In general, ForC contained roughly comparable information on C fluxes in regrowth vs mature forests, with the notable exception of tropical forests, for which there were no fluxes that had been measured in $\ge$ 7 different geographic areas. C stocks were better documented for regrowth stands, with a total of # records from # distinct geographic areas. Both C stocks and fluxes commonly displayed significant trends with stand age for within-biome analyses (Fig. 5-10; detailed below). Differences across biomes typically paralleled those observed for mature forests, with C cycling generally most rapid in the tropics and slowest in boreal forests (Figs. 5-6).

(**check paragraph with latest data**) ForC contained 14 flux variables with sufficient data for cross-biome analyses of age trends in regrowth forests (see Methods) (Fig. 5-6 and **S#- SI figures including plots for all variables**). Of these, 9 increased significantly with log10[stand.age]: $GPP$, $NPP$, $ANPP$, $ANPP_{foliage}$, $ANPP_{woody}$, $ANPP_{woody-stem}$, $BNPP$, $BNPP_{root-fine}$, $R_{eco}$, and net C sequestration ($NEP$). The remaining five--$ANPP_{woody-branch}$, $BNPP_{root-coarse}$, $R_{soil-het}$, and $R_{soil-het}$-–displayed no significant relationship to stand age, although all displayed a positive trend. In terms of C stocks, 10 variables had sufficient data to test for age trends. Six of these—total biomass, aboveground biomass, aboveground woody biomass, foliage biomass, root biomass, and coarse root biomass—increased significantly with $log10[stand.age]$. The remaining four displayed non-significant positive trends:  fine root biomass, total dead wood, standing dead wood, and organic layer.

\newpage
\blandscape
```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 7 | C cycle diagram for young tropical broadleaf forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. When age trends are signficant, they are presented with numbered equations; otherwise, means are presented. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}

@@

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 8 | C cycle diagram for young temperate broadleaf forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. When age trends are signficant, they are presented with numbered equations; otherwise, means are presented. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}

@@

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 9 | C cycle diagram for young temperate conifer forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. When age trends are signficant, they are presented with numbered equations; otherwise, means are presented. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}

@@

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 10 | C cycle diagram for young boreal conifer forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. When age trends are signficant, they are presented with numbered equations; otherwise, means are presented. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}

@@

ForC v.XX yielded a fairly comprehensive and internally consistent picture of C cycling in the world's major forest biomes. 
Carbon cycling rates generally increased from boreal to tropical regions and with stand age. 
Specifically, the major C fluxes were highest in tropical forests, intermediate in temperate (broadleaf or conifer) forests, and lowest in boreal forests -- a pattern that generally held for regrowth as well as mature forests (Figs. 5-6). 
In contrast to C fluxes, there was little directional variation in mature forest C stocks across biomes (Figs. 1-4, 6). 
The majority of flux variables, together with most live biomass pools, increased significantly with stand age (Figs. 5-10). 
Together, these results indicate that, moving from cold to tropical climates and from young to old stands, there is a general acceleration of C cycling, whereas C stocks of mature forests are influenced by a different set of drivers.

@@

* C cycle closure is fairly good. 
* However, SD's are often large, reflective of significant within-biome variation. This makes the standard for closure relatively loose.
* Lack of closure, in the few instances where it occurs, is probably more reflective of differences in the representation of forest types (e.g., disproportionate representation of US Pacific NW for aboveground woody biomass relative to AGB; Fig. 3) than of methodological accuracy.

@@

>>>>

Here, we synthesize ForC data (Fig. 1) to provide a macroscopic overview of stand-level carbon cycling of the world’s major forest biomes and how it varies with stand age. We address three broad questions:

@@

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 1 | Map of sites included in this analysis. Symbols are colored according to the number of records at each site. Underlying map shows coverage of evergreen, deciduous, and mixed forests (from SYNMAP; Jung et al. 2006) and biomes. Distribution of sites, plots, and records among biomes is shown in the inset.", out.width='100%', fig.pos='H'}

  knitr::include_graphics("tables_figures/World_Map_records_in_Biomes.png")
```

@@

This review synthesizes data from the ForC database [Fig. 1; https://github.com/forc-db/ForC; @anderson-teixeira_carbon_2016, @anderson-teixeira_forc_2018]. ForC amalgamates numerous intermediary data sets (*e.g.*, REFS) and original studies. 
Original publications were referenced to check values and obtain information not contained in intermediary data sets, although this process has not been completed for all records. 
The database was developed with goals of understanding how C cycling in forests varies across broad geographic scales and as a function of stand age. 
As such, there has been a focus on incorporating data from regrowth forests (*e.g.*, Anderson et al 2006, Martin et al 2013, Bonner et al 2013) and obtaining stand age data when possible (83% of records in v.2.0; Anderson-Teixeira et al 2018). 
Particular attention was given to developing the database for tropical forests [@anderson-teixeira_carbon_2016], yet these represented only approximately one-third of records in ForC v.2.0 [@anderson-teixeira_forc_2018]. 
Since publication of ForC v.2.0, we added the following data to ForC: the Global Database of Soil Respiration Database [SRDB v.##; @bond-lamberty_global_2010], the Global Reforestation Opportunity Assessment database (GROA v1.0; Cook-Patton et al. in press; ZenodoDOI), and data from several publications (Taylor et al. 2017, Lutz et al. 2018, Johnson_2018_csss; see GitHub repo for complete list) ([GitHub list](https://github.com/forc-db/ForC/blob/master/database_management_records/ForC_data_additions_log.csv)). 
We note that there remains a significant amount of relevant data that is not yet included in ForC, particularly biomass data from national forest inventories (*e.g.*,: REFS). 
The database version used for this analysis has been tagged as a new release on Github (XX) and assigned a DOI through Zenodo (DOI: TBD).

@@

We drew upon records for *#* annual flux and *#* C stock variables (Table 1). For this analysis, we combined some of ForC’s specific variables (*e.g.*, multiple variables for net primary productivity including various components) into more broadly defined variables (Table 1, [this table](https://github.com/forc-db/ForC/blob/master/figures/C_cycle_diagrams/ForC_variables_mapping_for_C_cycle_diagrams.csv))). 
Although ForC contains information that may be used to standardize or control for methodological differences [*e.g.*, area sampled, min stem diameter sampled, allometric equations applied; @anderson-teixeira_forc_2018], for this analysis we included all relevant data in ForC. 
Throughout ForC, for all measurements drawing from tree census data (*e.g.*, biomass, productivity), the minimum stem diameter sampled was $\le$ 10cm. All records were measured directly or derived from field measurements (as opposed to modeled).

@@

Data were analyzed to produce basic summaries of C cycle patterns across biomes and stand ages following an approach similar to that of Anderson-Teixeira et al (2016). 
For mature forests, to obtain the values reported in the C cycle schematics, we first averaged any repeated measurements within a plot, weighting flux measurements according to the length of measurement periods (*i.e.*, end.date - start.date). 
Values were then averaged across plots clustered within 25 km of one another (geographic.area field of SITES table, sensu Anderson-Teixeira et al 2018), weighting by area.sampled (MEASUREMENTS table) or plot.area (PLOTS table) if available for all records. 
This step was taken to avoid pseudo-replication and to combine any records from sites with more than one name in ForC. 
Finally, for figures 6 and 7, the original values were analyzed via a linear mixed effects model ('lmer' function in 'lme4' R package) with biome as fixed effect and plot nested within geographic.area as random effects on the intercept. 
When Biome had a significant effect, we looked at a Tukey's pairwise comparison to see which biomes were significantly different from one another. There were enough data to run this analysis for all focal variables but **biomass_ag_understory, BNPP_root.turnover_fine, deadwood_down, total.ecosystem_2.**

@@

Average C cycles for tropical broadleaf, temperate broadleaf, temperate conifer, and boreal forests $\ge$ 100 years old and with no known major disturbance or significant anthropogenic management are presented in Figures 2-5, and statistics for each biome type are also summarized at: [GitHub URL]. 
Of the 23 flux and 11 stock variables mapped in these diagrams, ForC contained estimates from $\ge$ 7 distinct geographic areas for *#* fluxes and *#* stocks in tropical broadleaf forests, *#* fluxes and *#* stocks in temperate broadleaf forests, *#* fluxes and *#* stocks in temperate conifer forests, and fluxes and *#* stocks in boreal forests. 
For variables with records from $\ge$ 7 distinct geographic areas, these ensemble C budgets were generally consistent. 
That is, component fluxes and stocks summed to within 1 std of more inclusive fluxes in all but one instance (in temperate conifer forests, $aboveground woody biomass + foliage biomass > aboveground biomass + 1std$; Fig. 5). **update this: https://github.com/forc-db/ERL-review/issues/16 **

\blandscape
```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 2 | C cycle diagram for mature tropical broadleaf forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data. Arrows are scaled as the **square root of flux divided by 5**.", out.width='100%', fig.pos='H'}

@@

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 4 | C cycle diagram for mature temperate conifer forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}

@@

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 5 | C cycle diagram for mature boreal conifer forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}

@@

(**check paragraph with latest data**) The largest C fluxes—including $GPP$, $NPP$, $ANPP$, $BNPP$, $R_{soil_het}$, $R_{soil}$, $R_{eco}$, — were highest in tropical forests, intermediate in temperate (broadleaf or conifer) forests, and lowest in boreal forests  ([ForC_variable_averages_per_Biome](https://github.com/forc-db/ForC/blob/master/numbers_and_facts/ForC_variable_averages_per_Biome.csv)) (Fig. 6). 
The same held true for some of the subsidiary fluxes: ANPP_foliage, ANPP_woody, [**OTHERS?**]. Other subsidiary fluxes—including NPP_woody, ANPP_repro, ANPP_stem, ANPP_branch, woody.mortality, BNPP_coarse, BNPP_fine,  [**OTHERS?**]—deviated from this pattern and/or lacked data for some biomes. 
Net ecosystem production ($NEP$) did not follow this pattern, with no significant differences across biomes but the largest average in temperate broadleaf forests, followed by temperate conifer, boreal, and tropical forests.
Thus, C cycling rates generally decreased from tropical to temperate to boreal forests, but with less apparent trends for some of the subsidiary fluxes and an important exception in the overall C balance ($NEP$).

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 6 | Age trends and biome differences in some of the major C fluxes: (a) $GPP$, (b) $NPP$, (c) $ANPP$, (d) $R_{soil}$, (e) $R_{eco}$, and (f) $NEP$. Map shows data sources ($x$ and $o$ indicate young and mature stands, respectively). Lines...  .", out.width='100%', fig.pos='H'}

  knitr::include_graphics("tables_figures/Flux_age_trends.png")
```

There were less distinct trends in C stocks across biomes (Fig. 7). 
Biome means for live aboveground and total biomass followed the same general trend as the major fluxes, with biomass of tropical= temperate broadleaf $\ge$ temperate conifer> boreal forests (Fig. 7a). 
However, the relative differences in these means were much smaller than for the major C fluxes, and there was significant variation within biomes. 
Maximum aboveground biomass values followed a very different trend than the means: temperate broadleaf> temperate conifer>boreal>tropical. 
There were some statistically significant biome differences in less frequently sampled C stocks (*e.g.*, woody biomass, foliage biomass, deadwood), but given high within-biome variability in C stocks and relatively low sample sizes, these were likely attributable to sampling biases and methodological differences than to true differences across biomes.

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 7 | Age trends and biome differences in some of the major forest C stocks: (a) aboveground biomass, (b) foliage, (c) fine roots, (d) dead wood.", out.width='100%', fig.pos='H'}

  knitr::include_graphics("tables_figures/Stock_age_trends.png")
```

@@

(**check paragraph with latest data**) Average C cycles for forests <100 years old are presented in Figures 8-11. In general, ForC contained roughly comparable information on C fluxes in regrowth vs mature forests, with the notable exception of tropical forests, for which there were no fluxes that had been measured in $\ge$ 7 different geographic areas. C stocks were better documented for regrowth stands, with a total of # records from # distinct geographic areas. Both C stocks and fluxes commonly displayed significant trends with stand age for within-biome analyses (Fig. 5-10; detailed below). Differences across biomes typically paralleled those observed for mature forests, with C cycling generally most rapid in the tropics and slowest in boreal forests (Figs. 6-7).

(**check paragraph with latest data**) ForC contained 14 flux variables with sufficient data for cross-biome analyses of age trends in regrowth forests (see Methods) (Fig. 6-7 and **S#- SI figures including plots for all variables**). Of these, 9 increased significantly with log10[stand.age]: $GPP$, $NPP$, $ANPP$, $ANPP_{foliage}$, $ANPP_{woody}$, $ANPP_{woody-stem}$, $BNPP$, $BNPP_{root-fine}$, $R_{eco}$, and net C sequestration ($NEP$). The remaining five--$ANPP_{woody-branch}$, $BNPP_{root-coarse}$, $R_{soil-het}$, and $R_{soil-het}$-–displayed no significant relationship to stand age, although all displayed a positive trend. In terms of C stocks, 10 variables had sufficient data to test for age trends. Six of these—total biomass, aboveground biomass, aboveground woody biomass, foliage biomass, root biomass, and coarse root biomass—increased significantly with $log10[stand.age]$. The remaining four displayed non-significant positive trends:  fine root biomass, total dead wood, standing dead wood, and organic layer.

\newpage
\blandscape
```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 8 | C cycle diagram for young tropical broadleaf forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. When age trends are signficant, they are presented with numbered equations; otherwise, means are presented. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}

@@

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 9 | C cycle diagram for young temperate broadleaf forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. When age trends are signficant, they are presented with numbered equations; otherwise, means are presented. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}

@@

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 10 | C cycle diagram for young temperate conifer forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. When age trends are signficant, they are presented with numbered equations; otherwise, means are presented. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}

@@

```{r echo=FALSE, fig.align = "center", fig.cap = "Figure 11 | C cycle diagram for young boreal conifer forests. All units are Mg C ha$^{-1}$ yr$^{-1}$ (fluxes) or Mg C ha$^{-1}$. Presented are mean ± std, where geographically distinct areas are treated as the unit of replication.  Arrows indicate fluxes, boxes indicate stocks. When age trends are signficant, they are presented with numbered equations; otherwise, means are presented. Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data.", out.width='100%', fig.pos='H'}

@@

ForC v.XX yielded a fairly comprehensive and internally consistent picture of C cycling in the world's major forest biomes. 
Carbon cycling rates generally increased from boreal to tropical regions and with stand age. 
Specifically, the major C fluxes were highest in tropical forests, intermediate in temperate (broadleaf or conifer) forests, and lowest in boreal forests -- a pattern that generally held for regrowth as well as mature forests (Figs. 6-7). 
In contrast to C fluxes, there was little directional variation in mature forest C stocks across biomes (Figs. 2-5, 7). 
The majority of flux variables, together with most live biomass pools, increased significantly with stand age (Figs. 6-11). 
Together, these results indicate that, moving from cold to tropical climates and from young to old stands, there is a general acceleration of C cycling, whereas C stocks of mature forests are influenced by a different set of drivers.

@@

* C cycle closure is fairly good. 
* However, SD's are often large, reflective of significant within-biome variation. This makes the standard for closure relatively loose.
* Lack of closure, in the few instances where it occurs, is probably more reflective of differences in the representation of forest types (e.g., disproportionate representation of US Pacific NW for aboveground woody biomass relative to AGB; Fig. 4) than of methodological accuracy.

@@

* note that our equations are unlikely to be the best possible for any given flux
